### 2019-07-26 paper/paper.tex
Update paper.tex

>>>>

\hrule
\textbf{Algorithm - Core.jl}
\hrule
 \begin{enumerate}

    \item[1.] \textit{\textbf{function} gsreg\_single\_proc\_results!(args…)}
    \begin{enumerate}
        \item[1.1.] Select regression covariates
        \item[1.2.] Perform QR Decomposition
        \item[1.3.] Estimate regression results
        \item[1.4.] Calculate additional tests
        \item[1.5.] Save individual results in a Shared Array
    \end{enumerate}
    \item[] \textbf{end} \textit{function gsreg\_single\_proc\_results!(args…)}

\vspace{2mm}

    \item[2.] \textit{\textbf{function} gsreg\_proc\_results!(args…)}
    \begin{enumerate}
        \item[2.1.] \textbf{for} $j=1$ : $((k^2-1)/ nworkers)$ \textit{\# where nworkers is the user defined number of cores, and k is the numbers of covariates in the GUM}
        \begin{enumerate}
            \item[2.1.1.] $order = (j -1) * nworkers + workerID$
            \item[2.1.2.] \textit{gsreg\_single\_proc\_results!(order, args...)}
        \end{enumerate}
        \item[] \textbf{end} for
    \end{enumerate}
    \item[] \textbf{end} \textit{function gsreg\_single\_proc\_results!(args…)}

\vspace{2mm}

    \item[3.] \textit{\textbf{function} proc!(args…)}
    \begin{enumerate}
        \item[3.1.] Create environment (Shared Array and other objects)
        \item[3.2.] for $workerID = 1:nworkers$
        \begin{enumerate}
            \item[3.2.1] spawn jobs among workerIDs to perform gsreg\_proc\_results!
        \end{enumerate}
        \item[] \textbf{end} for
        \item[3.3.] Perform vector operations
        \item[3.4.] Call \verb utils.jl  sort function
        \item[3.5.] Create results array
    \end{enumerate}
    \item[] \textbf{end} \textit{function proc!(args…)}

\vspace{2mm}

    \item[4.] Export results using \verb gsreg\_results.jl   structure
    \item[5.] Export summary results to a txt file 
    \item[6.] Optionally send the results structure to \verb utils.jl  to export a csv file.
  \end{enumerate}

\textbf{end} module \verb Core.jl .
